%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = black,
            citecolor = black,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}
\renewcommand{\baselinestretch}{1.10}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://www.linkedin.com/in/amol-suraj-mishra-598851125/}{Amol Suraj Mishra}}
\end{center}
\vspace{-6mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-8mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:amolsuraj.vit5@gmail.com}{amolsuraj.vit5@gmail.com} ~\textbullet~ \(+91\) 9994025766 ~\textbullet~ 1020, Men's Hostel - L Block, VIT Vellore, Vellore, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Objective}
Results-driven and diligent professional seeking a Software Engineer position with Core Concepts utilizing strong technical acumen, logical thinking and relevant expertise to provide the company with the best software solutions.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{M.Tech in Software Engineering, 5 year integrated} \hfill 2014 - Present \\
{Vellore Institute of Technology, Vellore, Tamil Nadu}\\
{CGPA - \textbf{9.72}/10 and Rank - \textbf{2}/475}\\
\textbf{High School} - {{DAV Public School, Hyderabad}} (CBSE) - \textbf{90\%} \hfill 2012 - 2014 \\
\textbf{Secondary School} - Karuna High School, Sangareddy (SSC) - \textbf{95\%} \hfill 2002 - 2012
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{\href{https://drive.google.com/file/d/18-PW1eimQVanLYkNC0zvCAAHwokeDYhB/view?usp=sharing}{Program Representative},{VIT University}} \hfill July, 2016 - Present \\
Representing the needs and expectations of my peer group to the management, regarding the curriculum operational requirements of the university by filling the gap between them and the management. \\
\\
\textbf{\href{https://drive.google.com/file/d/0B9TCAG7AVugiVUh4c0VQSWtKUUE/view?usp=sharing}{Summer Research Intern}, {IIT Bombay}} \\
\emph{Mentored by \href{http://en.wikipedia.org/wiki/Deepak_B._Phatak}{Prof. Deepak B Phatak, Dept. of CSE, IIT Bombay}} \hfill May, 2017 - July, 2017 \\
Research work for the enhancement of IITBombayX platform. Project was to create an \textbf{\href{https://github.com/amolmishra23/edx-adminxblock}{Open-edX server task automator}} using XBlock, which will perform all the tasks which a system administrator frequently performs in the lifecycle of the Open edX server. 

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Programming Languages }- R, Python, Java, C\#, C++, C, SQL\\
\textbf{Tools/Frameworks }- MATLAB, MySQL, Oracle database, Microsoft Office, Git, \LaTeX, Django\\
\textbf{Operating Systems } - Windows, Ubuntu\\
\textbf{Non-Technical } - Speaking, Presentation, Leadership, Content Writing, Management, Documentation

%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS
%----------------------------------------------------------------------------------------
\section{Selected Projects}
All projects available on git : \url{https://github.com/amolmishra23}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
 \item \textbf{\href{https://github.com/amolmishra23/CDAI}{Comprehensive data mining, visualization and predictive analysis on IPL using machine learning}} : Web application that performs detailed analysis and visualization of various features, ranking of players, prediction of match results built using IPL season 1 to 10 dataset in R language. 
 \item \textbf{\href{https://github.com/amolmishra23/coursera-data-science-capstone}{Swiftkey text prediction model}} : Web application that makes next-word prediction using the concept of n-grams in NLP,  built using textual data from twitter, news and blogs.
 \item \textbf{\href{https://github.com/amolmishra23/twitter-sentiment-analysis}{Sentiment Analysis using NLTK, TextBlob --- Comparison Study}} : Web application for getting the sentiment polarity of real-time tweets from Twitter and plotting them.
 \item \textbf{\href{https://github.com/amolmishra23/travel_assistance_vip}{Travel assistance system for a visually impaired person}} : This application makes the travel of a visually impaired person easy, when he travels on bus. Made using SERVLETS in JAVA.
 \item \textbf{\href{https://github.com/amolmishra23/TEXT-EDITOR}{Simple Text Editor in JAVA using AWT}} : Simple notepad like text editor with productive functionalities and shortcuts to fasten the process of preparing a text document made using JAVA AWT.
\end{itemize}

%----------------------------------------------------------------------------------------
%	CERTIFICATES SECTION
%----------------------------------------------------------------------------------------

\section{Certificates}

\begin{tabular}{l l}
John's Hopkins University(Coursera) & \textbf{\textit{\href{https://www.coursera.org/account/accomplishments/specialization/VRCB8VCQ9K3C}{Data Science Specialization (Series of 10 courses)}}} \\ [1pt]
Stanford University(Coursera) & \textbf{\textit{\href{https://www.coursera.org/account/accomplishments/certificate/64DD96W9XRG2}{Machine Learning}}} \\ [1pt]
University Of Michigan(Coursera) & \textbf{\textit{\href{https://www.coursera.org/account/accomplishments/certificate/W6EJKFQ79V96}{Getting Started with Python}}} \\ [1pt]
University Of Michigan(Coursera) & \textbf{\textit{\href{https://www.coursera.org/account/accomplishments/certificate/PTFCZM25G7JV}{Python Data Structures}}} \\ [1pt]
GDG VIT Vellore & \textbf{\textit{\href{https://drive.google.com/file/d/0B9TCAG7AVugiaUhONDl6ampCZ1E/view?usp=sharing}{Google Developers Android Study Jams}}} \\ [1pt]
\end{tabular}
 
%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achieve\-ments and Awards}
\hspace{1mm}{\textbf{\href{https://drive.google.com/file/d/1EB3Aiee04TLlCBgUBhZFDFhUXh_b7Ca4/view?usp=sharing}{Merit Scholarship Award}}} \hfill  2016,2017,2018\\
\hspace{1mm}{\textbf{\href{https://drive.google.com/file/d/1B7ddO4BN8pSATeUkQKvqLB2Zr75-8xoA/view?usp=sharing}{VIT Achiever's Award}}} \hfill  2018\\ 

\end{resume}
\end{document}